---
title: 'Week 5: Regression Modeling'
author: "YourNamesHere"
output: html_document
---

```{r setup, include=FALSE, warning=F, message=F}
library(tidyverse)
```

# Part 1: Linear Regression

## Introduction

LaQuinta is trying to decide where to locate a new motel.  As analysts, your team is tasked with determining which factors are relevant in determing profitability and predicting strong locations for expansion.  A group of strategists determined factors worthy of exploration are competition, market awareness, demand generators, socio-economic factors, and location.

In preparation, the company has identified and compiled a variety of potential predictors for profitability (measured via operating margin--Margin--of current hotels). They are:

* Number: Total motel and hotel rooms within a 3 mile radius
* Nearest: Number of miles to closest copmetition
* OfficeSpace: Volume of office space in surrounding community, in 1000s sqft 
* Enrollment: Number of college and university students in the community, in 1000s
* Income: Median household income, $1000s
* Distance: Distance (in miles) to the downtown core

## Exploratory Analysis

First, load the data and explore some features of interest.
```{r, warning = F, message = F}
laquinta <- read_csv("https://raw.githubusercontent.com/jddbucknole/SMB-A/master/LaQuinta.csv")
```

Examine the scatterplots relating the explanatory variables to the response (Margin) as well as the correlation.  Include a couple plots of interest and the correlation matrix.  Comment on what you see.  Which variables appear to be impactful in predicting margin? Which influence in a positive manner? Negative manner? Is that what you expected?


## Simple Linear Regression

Fit a linear model to predict Margin from the single variable that is the **most correlated** with the response.  Interpret both coefficients **in context** if they are sensible. If not, explain why not. You might find the `ggpairs` function in the `GGally` package useful to visualize the relationships among variables.

```{r}
deleteme <- 0
```


## Model Fitting

Fit a multiple linear regression model to predict Margin from the other predictors.  Produce the "best" model according to whatever criteria you choose.  After you have finalized your model, report the summary and any requisite diagnostic plots below (only run the final model in this R markdown file). 

```{r}
deleteme <- 0
```


## Conclusion and Recommendations

Discuss why you chose the model you settled on.  Focus on the model fit, residuals, significance, etc.  This is the most important part of the assignment. Make sure to give concrete recommendations to LaQuinta in context. You should use common business language explaining what factors are relevant without focusing solely on the statistical jargon.  

There is a location of interest that has 3815 rooms within 3 miles, the closest hotel is 0.9 miles away, the amount of office space  is 476,000 square feet, there is one college and one university with a total enrollment of 24,500, the median income in the area is $35,000, and the distance to the downtown core is 11.2 miles.  Form a 95% prediction interval for the profit margin at this location **based on your model**.  Profitable inns are defined by those with profit margins greater than 50\%. Would you recommend this site?

```{r}

deleteme <- 0
```


# Part 2: Logistic Regression

## Introduction
We will examine the data from the Tidy Tuesday dataset on [NYC Restaurant Inspections](https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-12-11). Our goal is to predict what conditions lead to a 'critical flag' from the health department.  This is a subsample including 50000 records (of the 300000 that were sampled for the Tidy Tuesday project).

```{r}
nyc <- read_csv('https://raw.githubusercontent.com/jddbucknole/ToolsProjects/main/nyc_sub.csv')
```

## Preliminary Analysis

As with any analysis, we should begin with an exploration of the data.  To accomplish this, complete the following tasks and summarize your findings below. If you'd like to create separate code blocks/summaries for each task, feel free to do so.

1. Filter the data to remove records with boro = 'Missing' or critical_flag = 'Not Applicable'.
2. Find the mean and standard deviation of score for each grade as well as the number of restaurants have received each grade.  Is a higher or lower score desired? Which grade has the most consistent scores? Visualize this with a side-by-side violin plot (`geom_violin()`) of scores by grade.
3. How do scores differ across boroughs (boro)? Make a side-by-side boxplot (or violin plot) of scores vs. borough.
4. Construct a summary of the percent of critical flags by borough (this can be accomplished with the `mean()` function on a logical statement).  Visualize this summary using the `geom_bin2d()` function to create a heatmap.

```{r}
deletme <- 0
```

## Logistic Regression

Our primary goal is to understand how score and borough relate to the occurence of a critical flag.  We would expect that higher scores are more likely to lead to a critical flag, but by how much? Should we worry about a small increase at the low score? What about at a high score? Are certain boroughs more likely to get flagged than others?

1. The `glm()` function requires the response variable to be 0/1. Using the `mutate()` and `ifelse()` functions, recode the critical_flag column as "Critical" = 1 and "Not Critical" = 0.
2. There are scores of -1 in this dataset (many of which contain violations).  Because this is an unknown value in the dataset, remove those records with a score < 0.
3. Run a logistic regression to predict the occurence of a critical flag as a function of borough (boro) and score.
4. Comment on the results of this model.  Which borough has the highest odds of critical flag after accounting for score? How does an increase in score of 1 unit affect the log odds of a critical flag? Comment below.

```{r}
deleteme <- 0
```

## Prediction

Tony Soprano is looking at opening a 'legitimate business establishment' in NYC (specifically Queens).  He is looking at buying a business with a score of 20 and doesn't want the health inspector to raise any questions.  For this specific restaurant, what is the *probability* that this restaurant will receive a critical flag? We will ignore the payoffs that certainly 'would **never** happen'.

```{r}
deleteme <- 0
```
