---
title: 'Week 3: Intro Data Wrangling'
author: 'Your names here'
output: 
  html_document:
    code_folding: show
---

Make sure that you have installed tidyverse. If the first knit doesn't work, run install.packages("tidyverse") in the console.

```{r setup, include=FALSE}
library(tidyverse)
```

## Part 1: R Markdown

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. Note that the text in the document is typed just like a normal Word document. 

To add code, we add a code chunk.  In the provided code chunk below, do the following:

1. Remove the code in the chunk.
2. Add 3 and 5 and save the result into the variable `easysum`.
3. Take the square root of 42 and don't save it.
4. Save the names of your group (characters) into a vector called `group_members`
5. Print the vector `group_members`

```{r part1}
delete_me <- 0
```

# Part 2: Data Wrangling

## Introduction

Bike sharing systems are rapidly becoming the norm in most big cities.  This analysis will examine data from the Capital Bike Share company in DC from 2011-2012. The goal is to have a better understanding of when people use the service and what we can do to be more efficient in deployment.  

First, examine the following [website](https://archive.ics.uci.edu/ml/datasets/bike+sharing+dataset) to get a better understanding for the background of the project and the dataset characteristics.  

## The Data

The dataset of daily usage and weather is loaded below.

```{r}
url_day <- "https://raw.githubusercontent.com/jddbucknole/bikesharing/master/bike_sharing-day.csv"
bike_day <- read.csv(url_day)
```

Explore the dataset a bit on your own here.  See what variables exist and what you may be interested in learning about. The function `str()` prints out the 'structure' of the data.  It gives the variable names and a few initial values.  Make sure you understand the key variables for analysis.  Think about what the key inputs and outputs are for the bike sharing company. No need to type any responses here.

```{r}
str(bike_day)
```


## Analysis

### Day of Week

Does daily ridership change based on day of the week? What about weekend and holiday use?

Using the bike_day dataset, find the average `cnt` of bikes grouped by day of the week.  Feel free to explore the workingday and holiday variables if you'd like as well. Make sure to understand which number represents which day of the week! Don't be afraid to look outside the data.

```{r}
deleteme <- 0

```

*Write a brief summary of your results in context.*


### Temperature

The temperature variable has been 'normalized' such that 0 is (close to) the lowest temperature recorded and 1 is the highest.  First, we will convert the temperature in the hourly dataset into a standard Celsius form for ease of interpretation then find the average number of users on days with freezing temperature (<0 C). 

1. Use the mutate function to create a new column `Temp_in_C = temp * 47 - 8` (see the website for details)
2. Filter for days below 0 temperature.
3. Find the average rider count.

Ideally, this is handled in a single piped set of commands without saving the intermediate steps.

```{r}
deleteme <- 0
```

*Comment on what you found*


### Weather 

I have coded the first 2 steps.  Examine the contents of `bike_day1` and `bike_day2` to see what is happening with the code.  From there, use the verbs we've learned to answer the question.

How does ridership change based on the weather? Also, does the weather impact casual and registered users use differently? To accomplish this, do the following:

1. Change the weathersit from 1-4 to the appropriate labels from the website above.  Use a mutate and either a series of nested ifelse statements (like you'd do in excel) or examine the `case_when` function.  Documentation can be found [here]("https://dplyr.tidyverse.org/reference/case_when.html").
2. Stack the number of casual and registered users into one column to form a tidy dataframe (one column for a label and one column for the counts).  This involves the `gather()` or `pivot_longer()` function.  I recommend using `pivot_longer()`
3. Use the appropriate dplyr verbs to summarize those data points to answer the question

```{r}
#I have separated these to allow you to see the output of these functions.
bike_day1 <- bike_day %>%
  mutate(weather = case_when(weathersit == 1 ~ "Clear, Partly Cloudy",
                             weathersit == 2 ~ "Mist",
                             weathersit == 3 ~ "Light Rain/Snow",
                             weathersit == 4 ~ "Heavy Rain/Snow")) 

bike_day2 <- bike_day1 %>%
  pivot_longer(cols = casual:registered, names_to = "Customer_Type", values_to = "Riders")
```

*Comment on what you found*


### Outliers

One day has a particularly low usage.  Use the appropriate verb this low usage day.  Once you have found the day, see if you can find out why this usage was so low (Google is a wonderful tool!). Do NOT print out the entire dataset!! If you'd like to print the top day, use the head() function or the top_n() function.

```{r}
deleteme <- 0
```

*Comment on what you found*


### Conclusion

*Write a few sentences about what you've learned by exploring this dataset and what may be of interest to the company going forward.*
