---
title: 'Week 1: RMarkdown & Intro R'
author: 'Your names here'
output: 
  html_document:
    code_folding: show
---

Make sure that you have installed tidyverse. If the first knit doesn't work, run install.packages("tidyverse") in the console.

```{r setup, include=FALSE}
library(tidyverse)
```

## Part 1: R Markdown

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. Note that the text in the document is typed just like a normal Word document. 

To add code, we add a code chunk.  In the provided code chunk below, do the following:

1. Remove the code in the chunk.
2. Add 3 and 5 and save the result into the variable `easysum`.
3. Take the square root of 42 and don't save it.
4. Save the names of your group (characters) into a vector called `group_members`
5. Print the vector `group_members`

```{r part1}
delete_me <- 0
```

### Summary stats and simple plots


Let's examine the TidyTuesday dataset on Philadelphia Parking Violations.  Please visit this [website](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-12-03) for more information about the data. This is a HUGE dataset, so it will take some time to load.



```{r philly}
tickets <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-03/tickets.csv")

```

Try adding `echo = FALSE` in the header of the chunk, reknit, and note the effect on the HTML document.


Now that the data is loaded, let's explore it a bit. Find the following:
1. The mean value of the fine using the mean() function
2. The top 5 violations in the violation_desc. FOr now, use the table() function and either sort or scan the table for the top 5.
3. The fine for "EXCESSIVE IDLING" 
4. A scatter plot of lat/lon using the following function `plot(tickets$lat, tickets$lon)`

```{r}
deleteme <-0
```

<Write a short summary of what you found. Call out the values requested above in a narrative structure (like a report).  Delete this line before submitting.>
