---
title: "Week 8: Text analytics"
author: "<your names here>"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(wordcloud)
library(textdata)
```

# Introduction

This week, we will examine the text of the Harry Potter books.  While I assume most have either read the books or seen the movies, that is not a requirement.  We will utilize the package `harrypotter` created by Bradley Boehmke and hosted on github.  Make sure to install the package prior to knitting this document. The package contains the raw text of all books separated by chapter.  The code below reads in all books and combines them into one dataset separated by book and chapter.  The columns `text` contains the entirety of the associated chapter.

Examine the code below and the resulting dataset `hpbooks`.  You should understand what is happening and get familiar with the end result.  For reference, `tibble` is the tidy version of `data.frame`.  It creates a tidy dataframe with the variables listed.  This is required because the package only provides the text in a character vector form. 


```{r}
library(harrypotter)

stone <- tibble(book = "1-Philosopher_Stone", numbook = 1, ch = 1:length(philosophers_stone), text = philosophers_stone)
chamber <- tibble(book = "2-Chamber_of_Secrets", numbook = 2,ch = 1:length(chamber_of_secrets), text = chamber_of_secrets)
prisoner <- tibble(book = "3-Prisoner_of_Azkaban", numbook = 3,ch = 1:length(prisoner_of_azkaban), text = prisoner_of_azkaban)
goblet <- tibble(book = "4-Goblet_of_Fire", numbook = 4,ch = 1:length(goblet_of_fire), text = goblet_of_fire)
phoenix <- tibble(book = "5-Order_of_the_Phoenix", numbook = 5,ch = 1:length(order_of_the_phoenix), text = order_of_the_phoenix)
prince <- tibble(book = "6-Half_Blood_Prince", numbook = 6,ch = 1:length(half_blood_prince), text = half_blood_prince)
hallows <- tibble(book = "7-Deathly_Hallows", numbook = 7,ch = 1:length(deathly_hallows), text = deathly_hallows)

hpbooks <- stone %>%
  bind_rows(chamber) %>%
  bind_rows(prisoner) %>%
  bind_rows(goblet) %>%
  bind_rows(phoenix) %>%
  bind_rows(prince) %>%
  bind_rows(hallows) 
```


# Part 1: Content of the Books/Chapters

This section will constitute a very simple dive into the words used in the books.  We won't explore context until part 2.  Expect to use a heavy dose of the tidyverse/ggplot techniques from the previous two weeks.

## How long are the books and which is the longest?

1. To begin, count how many total words (including stop words) are in the entire series.  This isn't going to be a perfect representation as the parsing isn't perfect in this dataset, but it should give a good estimate.

2. Count how many words are in each book and make a line chart with book name (or number) on the x-axis and the number of words on the y.  This graph should have the books in chronological order.  Make sure to have appropriate labels/titles. Note: you may need to include an aesthetic `group = 1` to make a line chart. 

```{r}
deleteme <- 0
```

## Top words

1. What are the top 10 words of the entire series (after removing stop words)?  Make a horizontal bar chart with the height (length) of the bar representing the frequency of the word.  Make sure to have appropriate labels/titles.  As your title will make it clear what is being plotted, you don't need an axis label for the words.  Also, make sure to display the bars in descending order of frequency.  Feel free to stem the words first if you'd like (optional).

```{r}
deleteme <- 0
```


2. You should notice that characters names appear more frequently that other words.  Add the characters names to the stop_words list and replot the top 10 words without character names.  The code below contains a list of characters.  Feel free to add to it.

```{r}
hp_characters <- c("harry", "ron", "hermione", "dumbledore", "sirius",
                     "mcgonagall", "snape", "hagrid", "voldemort",
                     "ginny","neville", "malfoy","crookshanks")

stop_words_characters <- stop_words %>%
  bind_rows(tibble(word = hp_characters, lexicon = "HP"))


##Your code

```


3. Focusing *only* on the characters in the list above. Make a faceted bar graph including ONLY those characters occurrence separated by book.  The output should look quite similar to the output of numbers 1 and 2, but include 7 different graphs.  Comment on how the series focus change (or didn't) over time.

```{r}
```

4. Make a wordcloud including the 100 most common words from the series (after removing stop_words--leave the characters names in there).  

```{r}
```

5. Find the average word length by book.  You can graph it or simply produce a table.  Word length is commonly used as a measure of 'complexity'.  How does the complexity change over the books?
```{r}

```

