---
title: 'Week 1: RMarkdown & Intro R'
author: 'Your names here'
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1: R Markdown

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. Note that the text in the document is typed just like a normal Word document. 

To add code, we add a code chunk.  In the provided code chunk below, do the following:

1. Remove the code in the chunk.
2. Add 3 and 5 and save the result into the variable `easysum`.
3. Take the square root of 42 and don't save it.
4. Save the names of your group (characters) into a vector called `group_members`
5. Print the vector `group_members`

```{r part1}
delete_me <- 0
```

### Summary stats and simple plots

You can also embed plots and create simple summary statistics. 

Let's examine the TidyTuesday dataset on Philadelphia Parking Violations.  Please visit this [website](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-12-03)




```{r philly}
tickets <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-03/tickets.csv")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
