---
title: "Week 5 Data Visualization"
author: "<your names here>"
output: html_document
---

```{r setup, warning = F, message = F}
library(tidyverse)
library(babynames)
library(scales)
library(ggrepel)
library(ggridges)
```

# Part 1 Movies!

```{r, warning = F, message = F}
movie <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-23/movie_profit.csv")
```

Let's take a look at a movie dataset. Make a column chart showing the Top 10 movies by worldwide gross. Recall that column charts require an x (categories) and y (bar height) aesthetic.  The bars should represent the respective worldwide gross of the movie *and be ordered by from largest to smallest*.  Note: this is handled by reordering factors (arrange will not be enough!). There is a function to assist in the `forcats` package that is included in `tidyverse`.  A simple google search should help.

Make use of the coord_flip() layer to make the labels readable and color code the bars (not just the outlines of the bars!) by the MPAA rating of the movie.  Finish with a short few sentences describing what you see.

```{r top10movies}
deleteme <- 0
```

**Description of findings**

Now, let's compare the average profits of the movies by genre.  Make a column chart in descending order to illustrate which genres yield the most returns (note: you have to create the profit column--assume worldwide_gross includes domestic_gross).

```{r profit}
```

Finally, we'll explore new aesthetics to examine the distribution of profit across genre.  For this, you'll make 3 plots:

1. A side-by-side boxplot of profits by genre
2. A side-by-side violin plot of profits by genre
3. A ridgeline plot of profits by genre.  Google ridgeline plots and `geom_density_ridges` from the `ggridges` packages for assistance.  

Special note: the 3 plots are all the same EXCEPT for the geom layer.

**Comment on the differences in the 3 outlays of the data and compare to the column chart of the mean**




# Part 2 Babynames

## Group name popularity

Create a graph showing the popularity of your group members first names over time. Make sure to account for the correct sex.

Here is an example for the Beatles. What name benefited from the appearance of the Fab Four?

<center> <img src = "https://github.com/jddbucknole/ToolsProjects/blob/main/beatles.png?raw=true">
</center>

```{r groupnames}
deleteme <- 0
```


